---
title: "Live Tutorial"
author: "Imperial"
date: "03/08/2019"
output: html_document
---

# R Markdown

### Code 1.1

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)

smaller <- diamonds %>% 
  filter(carat <= 2.5)
```

We have data about `r nrow(diamonds)` diamonds. Only `r nrow(diamonds) - nrow(smaller)` are larger than 2.5 carats. The distribution of the remainder is shown below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

### Code 1.2

```{r}
knitr::kable(
  mtcars[1:5, ], 
  caption = "Motor Trend Car Data"
)
```


### Code 2.1

1. Run ggplot(data = mpg).  What do you see?
```{r}
ggplot(data = mpg)
```

2. How many rows are in mpg?  How many columns/variables?
```{r eval = FALSE}
# Look up documentation
?mpg

# dim() function
dim(mpg)
str(mpg)
summary(mpg)
```

3. What does the **drv** variable describe?
```{r eval = FALSE}
# Look up documentation
?mpg
```

4. Make a scatter plot of hwy on the x-axis, cyl on y-axis.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = hwy, y = cyl))
```

5. Make a scatter plot of class vs. drv.  Why is this plot not very useful?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))

# The plot is not useful because of overplotting. Both class and drv are categrical variables. 
```


### Code 3.1

1. Run the following code. Why are the points not blue?
```{r}
ggplot(data = mpg)+ 
  geom_point(mapping = aes(x = displ, y = hwy, color="blue"))

# Because the colour is within aesthetics function. If you want to change the colour of all dots, put color = "blue" outside fo the aes() function.

```

2. What happens if you map an aesthetic something other than a variable name, like aes(color = disp <5?
```{r}
ggplot(data = mpg)+ 
  geom_point(mapping = aes(x = displ, y = hwy, color= displ<5))
```

### Code 3.2

```{r}
ggplot(data = mpg)+
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(vars(class), nrow = 2)
```

### Code 3.3

```{r}
ggplot(data = mpg)+
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(rows = vars(drv), cols = vars(cyl), labeller = label_both)
```

### Code 3.4

1. What happens if you facet on a continuous variable?

```{r eval=FALSE}
# It is possible, but not very useful. It may take awhile to process. 
ggplot(data = mpg)+
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(rows = vars(hwy), cols = vars(displ), labeller = label_both)
```


2. What does the following code produce? What does . do in the formula?

```{r eval=FALSE}
p <- ggplot(mpg, aes(displ, cty)) + geom_point()

# Use vars() to supply variables from the dataset:
p + facet_grid(rows = vars(drv))
p + facet_grid(cols = vars(cyl))
p + facet_grid(vars(drv), vars(cyl))

# The historical formula interface is also available:
p + facet_grid(drv ~ .)
p + facet_grid(. ~ cyl)
p + facet_grid(drv ~ cyl)
```

### Code 4.1

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() +
  geom_smooth(se = FALSE, show.legend = FALSE)
```

### Code 5.1

1. What parameters to geom_jitter() control the amount of displacement?
```{r eval=FALSE}
?geom_jitter
# Example
ggplot(mpg, aes(cty, hwy)) + 
  geom_jitter(width = 0.5, height = 0.5)
```

2. Try reproducing the following plot. (Hint: look up coord_flip()) 
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "fill") +
  coord_flip()
```

